\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-26 OaklandSubmission/impl.tex

\section{Implementation}
\label{sec:impl}
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
library~\cite{aby}. We use the default options of ABY except 
for the maximum number of gates. Our benchmarks require us to set this value to a
hundred million. ABY provides facilities to use multiple threads\footnote{The protocol has an offline phase and an online phase. Although multiple threads can be used in the offline phase, the online phase is single threaded.}.
We use at most four threads in our evaluation.

@@

Some of our benchamrks require accessing arrays at secret location.
For example, consider the expression $A[x]$ where $A$ is an array of size 2 and $x$ is shared.
\tool enforces the array indices to be public. The developer expresses this functionality in \tool
as $x > 0 ? A[1] : A[0]$. In general, for an array of size $2^n$, we need to write $2^{n-1}$ multiplexers
in \tool. This design choice of making secret indexing inconvinient to implement was deliberate.
Accessing arrays at secret locations is a powerful but expensive primitive
and we want the developers to perform this operation sparingly.

The secure code partitioning is not fully automatic.
in particular, the developer needs to decompose a program $P$ into $P_1||\ldots||P_k$ manually (Section~\ref{sec:pipe}). Then \tool generates $Q_1||\ldots||Q_k$ automatically.
Automating the decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave the construction of such
an analysis as future work.

The compilation rules of Figure~\ref{fig:compile} can introduce redundant coercions from arithmetic to
bool and vice versa.
The implemntation of \tool performs several optimizations to reduce these.
For example, on each coercion, \tool memoizes the pair of arithmetic share and boolean share involved in the coercion.
\tool invalidates such pairs when the variables corresponding to the shares are overwritten by assignments.
In subsequent coercions, \tool can reuse valid pairs (if available) instead of recomputing them afresh.

>>>>

\section{Implementation}
\label{sec:impl}
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
library~\cite{aby}. We set the security paramenter to 128 and use OT extension-based arithmetic multiplication triples generation. ABY provides facilities to use multiple threads\footnote{The protocol has an offline phase and an online phase. Although multiple threads can be used in the offline phase, the online phase is single threaded.}. We use at most four threads in our evaluation.

The current language implementation supports the following operators:
addition, subtraction, multiplication, division by powers of two, left shift,
logical and arithmetic right shifts, bitwise-(and, or, xor), unary negation,
bitwise negation. Because of its high cost, general division is not supported natively by \tool.
However, it can be implemented in about 30 lines.

@@

Some of our benchamrks require accessing arrays at secret location.
For example, consider the expression $A[x]$ where $A$ is an array of size 2 and $x$ is shared.
\tool enforces the array indices to be public. The developer expresses this functionality in \tool
as $x > 0 ? A[1] : A[0]$. In general, a secret access to an array of size $2^n$ requires $2^{n}-1$ multiplexers in \tool. Secure code partitioning currently requires a manual step.
In particular, the developer needs to decompose a program $P$ into $P_1||\ldots||P_k$ manually (Section~\ref{sec:pipe}). Then \tool generates $Q_1||\ldots||Q_k$ automatically.
Automating the decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave the construction of such
an analysis as future work.

The compilation rules of Figure~\ref{fig:compile} can introduce redundant coercions from arithmetic to
bool and vice versa.
The \tool compiler performs several optimizations to reduce these.
For example, on each coercion, \tool memorizes the pair of arithmetic share and boolean share involved in the coercion.
\tool invalidates such pairs when the variables corresponding to the shares are overwritten by assignments.
In subsequent coercions, \tool can reuse valid pairs (if available) instead of recomputing them afresh.

\divya{
\begin{enumerate}
\item add all the expressions that our language supports such as mult, bit-wise and and anything else.
\item Say that we compile to source to intermediate and use inter to circuit of ABY.. We can decide if we want to say this.
\end{enumerate}
}

### 2017-10-26 OaklandSubmission/ld.tex

\aseem{The target semantics models the semantics of the code output by
our compiler (C++ code in our implementation).}
A program in the intermediate language is evaluated to a circuit that can be executed in the distributed setting later. The evaluation to a circuit computes over the public parts of the program and also \emph{flattens} the arrays so that the circuits are unaware of the array structure. 
Crucially, this phase of the semantics does not have access to the secrets.
Below, we first provide the language for the circuits used followed by our evaluation rules.

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & \wire &&\\
    \ftext{Circuit gate} & \gate & ::= & \wire \mid \kw{in}^{m}_{j} \mid \kw{add}\:\gate_1\:\gate_{2} \mid \kw{gt}\:\gate_{1}\:\gate_{2}\\
    & & \mid & \kw{mux}\:\gate\:\gate_{1}\:\gate_{2} \mid \bval \rhd m\\
    \ftext{Base value} & \bval & ::= & c \mid \gate\\
    \ftext{Value} & \val & ::= & \bval \mid [\overline{\bval_{i}}]_{n}\\
    \ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho},x \mapsto \val \\
    \ftext{Circuit} & \crct & ::= & \cdot \mid \kw{bind}\:\gate\:\wire \mid \kw{out}\:\gate \mid \crct_{1}; \crct_{2}
  \end{array}
  \]
\caption{Circuits   \divya{Is environ misplaced? Can we merge base value and circuit gate?}}
\label{fig:circuits}
\end{figure}

\subsubsection*{Circuits}
\figureref{circuits} shows the circuits syntax. A wire id range
$\wire$ denotes a set of circuit wires that carry the value of a secret
shared variable in the output circuit (we will concretely define these
values later as part of the circuit semantics). Circuit gates $\gate$
are $\wire$, input gates, \kw{add}, \kw{gt}, and \kw{mux} gates, and
coerce gates $\bval \rhd m$. \divya{Gates are not just gates but a circuit?} Target values $\val$
then consist of base values $c$ and $\gate$, and arrays of base
values. \\

>>>>

As mentioned earlier, the intermediate language models the code such as in \figureref{ex-aby} output by our compiler. 
Next, a program in the intermediate language is evaluated to a circuit that can be executed in the distributed setting later. The evaluation to a circuit computes away the public parts of the program and also \emph{flattens} the arrays so that the circuits are unaware of the array structure. 
Crucially, this phase of the semantics does not have access to the secrets.
Below, we first provide the language for the circuits used followed by our evaluation rules.

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & \wire &&\\
    \ftext{Circuit gate} & \gate & ::= & \wire \mid \kw{in}^{m}_{j} \mid \kw{mult}\:\gate_1\:\gate_{2} \mid \kw{gt}\:\gate_{1}\:\gate_{2}\\
    & & \mid & \kw{mux}\:\gate\:\gate_{1}\:\gate_{2} \mid \bval \rhd m\\
    \ftext{Base value} & \bval & ::= & c \mid \gate\\
    \ftext{Value} & \val & ::= & \bval \mid [\overline{\bval_{i}}]_{n}\\
    \ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho},x \mapsto \val \\
    \ftext{Circuit} & \crct & ::= & \cdot \mid \kw{bind}\:\gate\:\wire \mid \kw{out}\:\gate \mid \crct_{1}; \crct_{2}
  \end{array}
  \]
\caption{Circuits   \divya{Is environ misplaced? Can we merge base value and circuit gate?}}
\label{fig:circuits}
\end{figure}

\subsubsection*{Circuits}
\figureref{circuits} shows the circuits syntax. A wire id range
$\wire$ denotes a set of circuit wires that carry the value of a secret
shared variable in the output circuit (we will concretely define these
values later as part of the circuit semantics). Circuit gates $\gate$
are $\wire$, input gates, \kw{mult}, \kw{gt}, and \kw{mux} gates, and
coerce gates $\bval \rhd m$. \divya{Gates are not just gates but a circuit?} Target values $\val$
then consist of base values $c$ and $\gate$, and arrays of base
values. \\
